Data Exploration: IUCN and AquaMaps

### 2015-11-23 data_explore.Rmd
added maps of species from iucn and aquamaps datasets

>>>>

```
***

###Global representation of species

By counting the number of unique species are found in each of the half degree cells we can then create a single global raster of number of species.

```{r map, echo=F, warning=F, message=F}

# Number of aquamaps species per cell

am_n_per_cell = filter(am_spp_cells,am_sid %in% unique(spp_list$am_sid))%>%
                  group_by(loiczid)%>%
                   summarize(count.am=n())%>%
                    as.data.frame()

am_sp_map = subs(loiczid_raster, am_n_per_cell[ , c('loiczid', 'count.am')], 
                     by = 'loiczid', 
                     which = 'count.am', 
                     subsWithNA = TRUE)

#number of IUCN species per cell
iucn_n_per_cell = iucn_spp_cells%>%
                   group_by(loiczid)%>%
                    summarize(count.iucn=n())%>%
                    as.data.frame()

iucn_sp_map = subs(loiczid_raster, iucn_n_per_cell[ , c('loiczid', 'count.iucn')], 
                     by = 'loiczid', 
                     which = 'count.iucn', 
                     subsWithNA = TRUE)

#Plot both maps
myTheme=rasterTheme(region=brewer.pal('Blues', n=9))

levelplot(am_sp_map,par.settings=myTheme,main='Aquamaps Dataset',colorkey=list( at=seq(0, 1063, length=15)))

levelplot(iucn_sp_map,par.settings=myTheme,main='IUCN Dataset',colorkey=list(at=seq(0, 1063, length=15)))
```

Now look at all aquamaps species

```{r all aquamaps,eval=F, echo=F}

am_spp_cells_big = fread(file.path(dir_anx, 'raw/aquamaps_2014/tables/ohi_hcaf_species_native.csv'))
#am_spp_cell_big is missing loiczid info so bring in hcaf to match

hcaf <- fread(file.path(dir_anx,'raw/aquamaps_2014/tables/hcaf.csv'))%>% #bring this in just to get loiczid
          as.data.frame()%>%
            select(CsquareCode,LOICZID)%>%
              rename(loiczid=LOICZID)

all_am = am_spp_cells_big%>%
          select(SpeciesID,CsquareCode)%>%
          group_by(CsquareCode)%>%
          summarize(count=n())%>%
          as.data.frame()

all = left_join(all_am,hcaf)

all_am_map = subs(loiczid_raster, all[ , c('loiczid', 'count')], 
                     by = 'loiczid', 
                     which = 'count', 
                     subsWithNA = TRUE)

levelplot(all_am_map,par.settings=myTheme,main='Entire Aquamaps Dataset')
```

![image](./figures/all_aquamaps_map.png)
